---
title: "MR Results"
author: "Shea Andrews"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    keep_md: true
    toc: true
    number_sections: false
    toc_depth: 4
    toc_float:
      collapsed: false
      smooth_scroll: false
params:
  MR_results.path: NA
  MRdat.path: NA
  mrpresso_global.path: NA
  mrpresso_global_wo_outliers.path: NA
  egger_comb.path: NA
  power.path: NA
  steiger.path: NA
  output.path: NA
  model: NA
  rwd: NA
  DATE: NA
  rlib: NA
  exposures: NA
  outcomes: NA
editor_options:
  chunk_output_type: console
---
```{r sandbox, eval=F}
# model <- "MR_ADphenome"
# model <- "MR_ADphenome_wo_apoe"
model <- "MR_ADbidir"
# DATE = "2020-07-27"
rwd = "/sc/arion/projects/LOAD/shea/Projects/MR_ADPhenome/"
DATE = Sys.Date()
setwd(rwd)

MR_results.path = glue("results/{model}/All/MRresults.txt")
MRdat.path = glue("results/{model}/All/mrpresso_MRdat.csv")
mrpresso_global.path = glue("results/{model}/All/global_mrpresso.txt")
mrpresso_global_wo_outliers.path = glue("results/{model}/All/global_mrpresso_wo_outliers.txt")
egger_comb.path = glue("results/{model}/All/pleiotropy.txt")
power.path = glue("results/{model}/All/power.txt")
steiger.path = glue("results/{model}/All/steiger.txt")
exposures = c("Dashti2019slepdur", "Day2018sociso", "Evangelou2018dbp", "Evangelou2018pp", "Evangelou2018sbp", 
              "Howard2019dep23andMe", "Jansen2018insomnia23andMe", "Klimentidis2018mvpa", "Lee2018education23andMe", 
              "Liu2019drnkwk23andMe", "Liu2019smkcpd23andMe", "Liu2019smkint23andMe", "Niarchou2020fish", "Niarchou2020meat", 
              "SanchezRoige2019auditt23andMe", "Wells2019hdiff", "Willer2013hdl", "Willer2013ldl", "Willer2013tc", 
              "Willer2013tg", "Xue2018diab", "Yengo2018bmi")
outcomes = c("Beecham2014braak4 Beecham2014npany", "Beecham2014vbiany", "Deming2017ab42", "Deming2017ptau", "Deming2017tau",
             "Grasby2020surfarea", "Grasby2020thickness", "Hilbar2015hipv", "Hilbar2017hipv", 
             "Huang2017aaos", "Kunkle2019load", "Lambert2013load")
```

```{r setup, echo=FALSE, message = FALSE, warning = FALSE}
message("Setup \n")
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = params$rwd)
.libPaths(c(params$rlib, .libPaths()))

library(tidyverse)
library(glue)
library(TwoSampleMR)
library(gridExtra)
library(qvalue)
library(here)
source(here("scripts", "miscfunctions.R"), chdir = TRUE)

```

```{r snakemake-input}
model = params$model
rwd = params$rwd
DATE = params$DATE
MR_results.path = params$MR_results.path
MRdat.path = params$MRdat.path
mrpresso_global.path = params$mrpresso_global.path
mrpresso_global_wo_outliers.path = params$mrpresso_global_wo_outliers.path
egger_comb.path = params$egger_comb.path
power.path = params$power.path
steiger.path = params$steiger.path
output.path = params$outfile
exposures = params$exposures
outcomes = params$outcomes
```


```{r load-data}
##  Read in R datasets
## Outcomes to include the results

## Files
message(glue("\n Loading: ", MR_results.path))
MR_results <- read_tsv(MR_results.path) %>%
  filter(exposure %in% exposures, outcome %in% outcomes)

message(glue("\n Loading: ", MRdat.path))
MRdat.raw <- read_csv(MRdat.path, guess_max = 100000) %>%
  filter(exposure %in% exposures, outcome %in% outcomes)

message(glue("\n Loading: ", mrpresso_global.path))
mrpresso_global <- read_tsv(mrpresso_global.path) %>%
  filter(exposure %in% exposures, outcome %in% outcomes)

message(glue("\n Loading: ", mrpresso_global_wo_outliers.path))
mrpresso_global_wo_outliers <- read_tsv(mrpresso_global_wo_outliers.path) %>%
  filter(exposure %in% exposures, outcome %in% outcomes)

mrpresso_global_comb <- bind_rows(mrpresso_global, mrpresso_global_wo_outliers)

message(glue("\n Loading: ", egger_comb.path))
egger_comb <- read_tsv(egger_comb.path) %>%
  rename(egger_se = se) %>%
    filter(exposure %in% exposures, outcome %in% outcomes)

message(glue("\n Loading: ", steiger.path))
steiger <- read_tsv(steiger.path) %>%
  filter(exposure %in% exposures, outcome %in% outcomes)

message(glue("\n Loading: ", power.path))
power <- read_tsv(power.path) %>%
  filter(exposure %in% exposures, outcome %in% outcomes) %>%
  select(exposure, outcome, pt, outliers_removed, pve.exposure, F, Power) %>%
  mutate(pve.exposure = round(pve.exposure*100, 2),
         F = round(F, 2),
         Power = round(Power, 2))

message(glue("\n Exposure - Outcome Pairs"))
exposures_outcomes <- expand_grid(exposures, outcomes) %>%
  magrittr::set_colnames(c("exposures.name", "outcomes.name")) %>%
  left_join(select(samplesize, code, trait, domain), by = c('exposures.name' = 'code')) %>%
  rename(exposure.name = trait, domain.exposure = domain) %>%
  left_join(select(samplesize, code, trait, domain), by = c('outcomes.name' = 'code')) %>%
  rename(outcome.name = trait, domain.outcome = domain)

if(model == "MR_ADbidir"){
  exposures_outcomes <- exposures_outcomes %>%
  mutate(domain.outcome = fct_relevel(domain.outcome, "Psychosocial", "Health", "Lifestyle"),
         domain.exposure = fct_relevel(domain.exposure, "Diagnosis", "CSF", "Neuropathology", "Neuroimaging")) %>%
         select(-exposures.name, -outcomes.name)
} else if(str_detect(model, "MR_ADphenome")){
  exposures_outcomes <- exposures_outcomes %>%
  mutate(domain.exposure = fct_relevel(domain.exposure, "Psychosocial", "Health", "Lifestyle"),
         domain.outcome = fct_relevel(domain.outcome, "Diagnosis", "CSF", "Neuropathology", "Neuroimaging")) %>%
         select(-exposures.name, -outcomes.name)
}

```

Aggregate report of the results of a MR analysis examining the causal effect of a given exosure on an outcome.

## Exposures-Outcomes

The following exposures were included in the analysis.
```{r print-exposure}
exposure.df <- filter(samplesize, code %in% (distinct(MR_results, exposure) %>% pull(exposure)))

exposure.df %>%
  DT::datatable(caption = "Table 1: Exposures",
                options = list(
                  pageLength = 5, autoWidth = TRUE, scrollX = T
                )
  )
```

<br> To investigate their causal effect on the follow outcomes

```{r print-outcome}
outcome.df <- filter(samplesize, code %in% (distinct(MR_results, outcome) %>% pull(outcome)))

outcome.df %>%
  DT::datatable(caption = "Table 2: Outcomes",
                options = list(
                  pageLength = 5, autoWidth = TRUE, scrollX = T
                )
  )
```

<br> The number of instruments avaliable for each exposure.

```{r print-mrpairs}
MR_results %>%
  filter(outliers_removed == FALSE, method == "Inverse variance weighted (fixed effects)") %>%
  group_by(exposure, pt) %>%
  summarise(n_outcome = n_distinct(outcome), min_nsnp = min(nsnp), mean_nsnp = mean(nsnp), max_nsnp = max(nsnp)) %>%
  mutate_at(vars("min_nsnp", "mean_nsnp", "max_nsnp"), round, 1) %>%
  pivot_wider(names_from = "pt", values_from = c("n_outcome", "min_nsnp", "mean_nsnp", "max_nsnp")) %>%
  select(exposure, ends_with("06"), ends_with("08")) %>%
  magrittr::set_colnames(str_replace(colnames(.), "_5e-06|_5e-08", "")) %>%
  DT::datatable(filter = 'bottom',
                caption = "Table 3: Number of SNPs avaliable in for each exposure",
                options = list(
                  pageLength = 5, autoWidth = TRUE, scrollX = T
                )
  )

```


## Harmonized exposure-outcome SNP dataset

```{r merge-data}
MRdat <- MRdat.raw  %>%
  ## Merge Sample Size information
  select(-samplesize.outcome, -samplesize.exposure) %>%
  left_join(select(samplesize, -pmid), by = c('exposure' = 'code')) %>%
  rename(samplesize.exposure = samplesize,
         ncase.exposure = ncase,
         ncontrol.exposure = ncontrol,
         logistic.exposure = logistic,
         exposure.name = trait,
         domain.exposure = domain,
         prevelance.exposure = prevelance) %>%
  left_join(select(samplesize, -pmid), by = c('outcome' = 'code')) %>%
  rename(samplesize.outcome = samplesize,
         ncase.outcome = ncase,
         ncontrol.outcome = ncontrol,
         logistic.outcome = logistic,
         outcome.name = trait,
         domain.outcome = domain,
         prevelance.outcome = prevelance)

```

```{r print-mrdat, eval=FALSE}
MRdat %>%
  select(exposure, outcome, pt, everything(), -id.outcome, -id.exposure) %>%
  mutate(pt = as.character(pt)) %>%
  mutate_if(is.numeric, signif, 2) %>%
  DT::datatable(filter = 'bottom',
                caption = "Table 4: Harmonized SNPs",
                options = list(
                  pageLength = 5, autoWidth = TRUE, scrollX = T
                )
  )
```

```{r write-harmonized-data, echo=FALSE, eval=TRUE}
write_csv(MRdat, glue("results/{model}/All/{model}_HarmonizedDatasets_{DATE}.csv"))
```


## MR Resuts

```{r mrsummary}
MRsummary <- MR_results %>%
  mutate(method = str_replace(method, "Inverse variance weighted \\(fixed effects\\)", 'IVW'),
         method = str_replace(method, "MR Egger", 'Egger'),
         method = str_replace(method, "Weighted median", 'WME'),
         method = str_replace(method, "Weighted mode", 'WMBE')) %>%
  rename(MR.pval = pval) %>%
  ## Join MR-PRESSO Global results
  left_join(select(mrpresso_global_comb, outcome, exposure, pt, RSSobs, pval, outliers_removed),
            by = c('outcome', 'exposure', 'pt', 'outliers_removed')) %>%
  rename(MRPRESSO.pval = pval) %>%
  ## Join Egger Intercept results
  left_join(select(egger_comb, outcome, exposure, pt, egger_intercept, egger_se, pval, outliers_removed),
            by = c('outcome', 'exposure', 'pt', 'outliers_removed')) %>%
  rename(Egger.pval = pval) %>%
  select(outcome, exposure, pt, method, outliers_removed, nsnp, n_outliers, b, se, MR.pval,
         RSSobs, MRPRESSO.pval, egger_intercept, egger_se, Egger.pval) %>%
  arrange(outcome, exposure, pt, method, outliers_removed) %>%
  ## Join Steiger
  left_join(select(steiger, outcome, exposure, pt, outliers_removed,
                   snp_r2.exposure, snp_r2.outcome, correct_causal_direction, steiger_pval),
          by = c('outcome', 'exposure', 'pt', 'outliers_removed')) %>%
  ## Merge Sample Size information
  left_join(select(samplesize, code, trait, domain), by = c('exposure' = 'code')) %>%
  rename(exposure.name = trait,
         exposure.domain = domain) %>%
  left_join(select(samplesize, code, trait, domain), by = c('outcome' = 'code')) %>%
  rename(outcome.name = trait,
         outcome.domain = domain)
```

```{r print-mrres}

MRsummary %>%
  select(exposure, outcome, pt, outliers_removed, nsnp, n_outliers, method, everything(), -outcome.name, -exposure.name, -outcome.domain, -exposure.domain) %>%
  mutate(pt = as.character(pt)) %>%
  mutate_if(is.numeric, signif, 2) %>%
  DT::datatable(caption = "Table 5: MR results",
                filter = 'bottom', options = list(
                pageLength = 5, autoWidth = TRUE, scrollX = T
                )
  )

```

```{r, eval=TRUE}
write_csv(MRsummary, glue("results/{model}/All/{model}_MRsummary_{DATE}.csv"))
```

```{r spread-res}
## Spread by methods
mrresults.methods <- MRsummary %>%
  mutate(b = signif(b, 2),
         se = signif(se, 2),
         MR.pval = signif(MR.pval, 2),
         RSSobs = round(RSSobs, 1),
         egger_intercept = signif(egger_intercept, 3),
         egger_se = signif(egger_se, 2),
         Egger.pval = signif(Egger.pval, 2)) %>%
  pivot_wider(names_from = method, names_glue = "{method}_{.value}", values_from = c(b, se, MR.pval)) %>%
 # myspread(method, c(b, se, MR.pval)) %>%
  mutate(IVW_Signif = as.character(signif.num(IVW_MR.pval)),
         Egger_Signif = as.character(signif.num(Egger_MR.pval)),
         WME_Signif = as.character(signif.num(WME_MR.pval)),
         WMBE_Signif = as.character(signif.num(WMBE_MR.pval)))

## Spread by outlier removal MR-PRESSO
mrresults.methods_presso <- mrresults.methods %>%
  left_join(power) %>%
  myspread(outliers_removed,
           c(nsnp, n_outliers, pve.exposure, F, Power, RSSobs, MRPRESSO.pval, 
             egger_intercept, egger_se, Egger.pval, 
             snp_r2.exposure, snp_r2.outcome, correct_causal_direction, steiger_pval,
             IVW_b, IVW_MR.pval, IVW_se, 
             Egger_b, Egger_MR.pval, Egger_se, 
             WME_b, WME_MR.pval, WME_se,
             WMBE_b, WMBE_MR.pval, WMBE_se, 
             IVW_Signif, Egger_Signif, WME_Signif, WMBE_Signif)) %>%
  arrange(pt, outcome, exposure) %>%
  arrange(outcome.name, exposure.name, pt) %>%
  select(outcome, exposure, outcome.name, exposure.name, pt, FALSE_nsnp, FALSE_pve.exposure, FALSE_F, FALSE_n_outliers,
         FALSE_snp_r2.exposure, FALSE_snp_r2.outcome, FALSE_correct_causal_direction, FALSE_steiger_pval,
         FALSE_IVW_b, FALSE_IVW_se, FALSE_IVW_MR.pval, FALSE_IVW_Signif, FALSE_Power,
         FALSE_Egger_b, FALSE_Egger_se, FALSE_Egger_MR.pval, FALSE_Egger_Signif,
         FALSE_WME_b, FALSE_WME_se, FALSE_WME_MR.pval, FALSE_WME_Signif,
         FALSE_WMBE_b, FALSE_WMBE_se, FALSE_WMBE_MR.pval, FALSE_WMBE_Signif,
         FALSE_RSSobs, FALSE_MRPRESSO.pval, FALSE_egger_intercept, FALSE_egger_se, FALSE_Egger.pval,
         TRUE_snp_r2.exposure, TRUE_snp_r2.outcome, TRUE_correct_causal_direction, TRUE_steiger_pval,
         TRUE_IVW_b, TRUE_IVW_se, TRUE_IVW_MR.pval, TRUE_IVW_Signif, TRUE_Power,
         TRUE_Egger_b, TRUE_Egger_se, TRUE_Egger_MR.pval, TRUE_Egger_Signif,
         TRUE_WME_b, TRUE_WME_se, TRUE_WME_MR.pval, TRUE_WME_Signif,
         TRUE_WMBE_b, TRUE_WMBE_se, TRUE_WMBE_MR.pval, TRUE_WMBE_Signif,
         TRUE_RSSobs, TRUE_MRPRESSO.pval, TRUE_egger_intercept, TRUE_egger_se, TRUE_Egger.pval) %>%
  magrittr::set_colnames(colnames(.) %>% str_replace(., "FALSE_", "") %>% str_replace(., "TRUE_", "outlier_"))
```


```{r print-res, knitr.kable.NA = '', eval=FALSE}

mrresults.methods_presso %>%
  select(-outcome, -exposure, -ends_with("Signif")) %>%
  mutate(pt = as.character(pt)) %>%
  knitr::kable(format = "html", table.attr = "class='dtable'") %>%
  kableExtra::kable_styling() %>%
  kableExtra::add_header_above(c(" " = 7, "IVW" = 4, "MR Egger" = 3, "WME" = 3, "WBE" = 3, " " = 5,  "IVW" = 4, "MR Egger" = 3, "WME" = 3, "WBE" = 3, " " = 5))  %>%
  kableExtra::scroll_box(width = "100%", height = "500px")

```

```{r, write-wide-MR-results}
WideMRResults <- mrresults.methods_presso %>%
  select(-outcome, -exposure, -ends_with("Signif")) %>%
  replace_na(., list(outlier_IVW_b = "", outlier_IVW_se = "", outlier_IVW_MR.pval = "", outlier_Power = "",
                     outlier_Egger_b = "", outlier_Egger_se = "", outlier_Egger_MR.pval = "",
                     outlier_WME_b = "", outlier_WME_se = "", outlier_WME_MR.pval = "",
                     outlier_WMBE_b = "", outlier_WMBE_se = "", outlier_WMBE_MR.pval = "",
                     outlier_RSSobs = "", outlier_MRPRESSO.pval = "",
                     outlier_egger_intercept = "", outlier_egger_se = "", outlier_Egger.pval = ""))

```

```{r, eval=TRUE}
write_csv(WideMRResults, glue("results/{model}/All/{model}_WideMRResults_{DATE}.csv"))
```


## Power Descriptive Statistics
Reportining the Median (min, max) for nsnps, PVE, F-statistic and power, for each exposure across all outcomes.


```{r power}
power_dsc <- mrresults.methods_presso %>% 
  select(outcome.name, exposure.name, pt, nsnp, pve.exposure, F, Power) %>%
  mutate_at(vars("nsnp", "pve.exposure", "F", "Power"), as.numeric) %>%
 # filter(pt == 5e-8) %>% 
  group_by(exposure.name, pt) %>% 
  summarise(min_nsnp = min(nsnp), 
            med_nsnp = median(nsnp),
            max_nsnp = max(nsnp),
            min_pve.exposure = min(pve.exposure), 
            med_pve.exposure = median(pve.exposure), 
            max_pve.exposure = max(pve.exposure), 
            min_Power = min(Power), 
            med_Power = median(Power), 
            max_Power = max(Power), 
            min_F = min(F), 
            med_F = median(F),
            max_F = max(F)) %>% 
  mutate(nsnp = glue("{med_nsnp} ({min_nsnp}, {max_nsnp})"), 
         pve = glue("{med_pve.exposure} ({min_pve.exposure}, {max_pve.exposure})"), 
         F = glue("{med_F} ({min_F}, {max_F})"), 
         power = glue("{med_Power} ({min_Power}, {max_Power})")) %>% 
  select(exposure.name, pt, nsnp, pve, F, power)


```

```{r, eval=TRUE}
write_csv(power_dsc, glue("results/{model}/All/{model}_DescriptivesPower_{DATE}.csv"))
```

```{r plot-power}
plc <- pals::polychrome() %>% .[3:36] %>% as.character() 
plc_df <- tibble(plc_colour = pals::polychrome() %>% .[3:36] %>% names(), 
                 plc_values = pals::polychrome() %>% .[3:36] %>% as.character())

mrresults.methods_presso %>% 
  select(outcome.name, exposure.name, pt, nsnp, pve.exposure, F, Power) %>%
  pivot_longer(cols = c(nsnp, pve.exposure, F, Power), names_to = "var", values_to = "value") %>%
  ggplot(., aes(x = value, y = exposure.name, colour = outcome.name)) + 
  geom_point() + facet_grid(pt ~ var, scales = "free") + 
  scale_color_manual(values = plc) +
  theme_bw() 
```


## Best results

```{r mrbest}
## -------------------------------------------------------------------------------- ##
##                      Filter results for MR-PRESSO and best PT                    ##
mr_res <- MRsummary %>%
  filter(method == 'IVW') %>%
  filter(nsnp > 2) %>%
  group_by(outcome, exposure) %>%
  filter(outliers_removed == ifelse(TRUE %in% outliers_removed, TRUE, FALSE)) %>%
  ungroup()

## Generate FDR values
qobj <- qvalue(p = mr_res$MR.pval, fdr.level = 0.1)
qvales.df <- tibble(pvalues = qobj$pvalues, lfdr = qobj$lfdr,
                    qval = qobj$qvalues, significant = qobj$significant)

mr_best <- mr_res %>%
  bind_cols(select(qvales.df, qval)) %>%
  group_by(outcome, exposure) %>%
  arrange(MR.pval) %>%
  slice(1) %>%
  ungroup() %>%
  select(outcome, exposure, pt, outliers_removed, qval) %>%
  left_join(mrresults.methods, by = c('outcome', 'exposure', 'pt', 'outliers_removed')) %>%
  mutate(MRPRESSO.pval_rm = as.numeric(str_replace(MRPRESSO.pval, '<', ""))) %>%
  mutate(pass = case_when(qval > 0.05 ~ FALSE,
                          MRPRESSO.pval_rm > 0.05 & Egger.pval > 0.05 ~ TRUE,
                          Egger_MR.pval < 0.05 | WME_MR.pval < 0.05 | WMBE_MR.pval < 0.05 ~ TRUE,
                          TRUE ~ FALSE),
         pass_0.1 = case_when(qval > 0.1 ~ FALSE,
                              qval < 0.05 ~ NA,
                              MRPRESSO.pval_rm > 0.05 & Egger.pval > 0.05 ~ TRUE,
                              Egger_MR.pval < 0.05 | WME_MR.pval < 0.05 | WMBE_MR.pval < 0.05 ~ TRUE,
                              TRUE ~ FALSE)
         )  %>%
  split(., 1:nrow(.)) %>%
  map_dfr(., function(x){
    x %>%
      mutate(pass = ifelse(pass == FALSE, FALSE, passfunc(IVW_MR.pval, IVW_b,
                                                          Egger_MR.pval, Egger_b,
                                                          WME_MR.pval, WME_b,
                                                          WMBE_MR.pval, WMBE_b)),
             pass_0.1 = ifelse(pass_0.1 == FALSE, FALSE, passfunc(IVW_MR.pval, IVW_b,
                                                                  Egger_MR.pval, Egger_b,
                                                                  WME_MR.pval, WME_b,
                                                                  WMBE_MR.pval, WMBE_b))
             )
  })  %>%
  left_join(select(samplesize, code, domain), by = c("exposure" = "code")) %>%
  left_join(select(samplesize, code, domain), by = c("outcome" = "code")) %>%
  rename(domain.exposure = domain.x, domain.outcome = domain.y)


if(model == "MR_ADbidir"){
  mr_best <- mr_best %>%
  mutate(domain.outcome = fct_relevel(domain.outcome, "Psychosocial", "Health", "Lifestyle"),
         domain.exposure = fct_relevel(domain.exposure, "Diagnosis", "CSF", "Neuropathology", "Neuroimaging"))
} else if(str_detect(model, "MR_ADphenome")){
  mr_best <- mr_best %>%
  mutate(domain.exposure = fct_relevel(domain.exposure, "Psychosocial", "Health", "Lifestyle"),
         domain.outcome = fct_relevel(domain.outcome, "Diagnosis", "CSF", "Neuropathology", "Neuroimaging"))
}

```

```{r, write-MRbest, eval=TRUE}
write_csv(mr_best, glue("results/{model}/All/{model}_MRbest_{DATE}.csv"))
```

```{r, mr-out}
out.final <- mr_best %>%
  mutate(IVW = paste0(IVW_b, '\n(',IVW_se, ')')) %>%
  mutate(`MR-Egger` = paste0(Egger_b, '\n(', Egger_se, ')', Egger_Signif)) %>%
  mutate(`Weighted median` = paste0(WME_b, '\n(',WME_se, ')', WME_Signif)) %>%
  mutate(`Weighted mode` = paste0(WMBE_b, '\n(',WMBE_se, ')', WMBE_Signif)) %>%
  select(outcome, exposure, outcome.name, exposure.name, pt, nsnp, n_outliers,
         snp_r2.exposure, snp_r2.outcome, correct_causal_direction, steiger_pval,
         IVW, qval, `MR-Egger`, `Weighted median`, `Weighted mode`,
         MRPRESSO.pval, Egger.pval, pass,
         -domain.exposure, -domain.outcome) %>%
  mutate(Egger.pval = round_sci(Egger.pval)) %>%
  mutate(qval = round_sci(qval)) %>%
  arrange(outcome.name, exposure.name) %>%
  mutate(nsnp = nsnp + n_outliers) %>%
  filter(as.numeric(qval) < 0.1) %>%
  arrange(outcome.name, exposure.name)

```

```{r, print-out}
mr_best %>%
  arrange(outcome.name, exposure.name) %>%
  filter(qval < 0.1) %>%
  mutate_at(vars(snp_r2.exposure, snp_r2.outcome, qval, Egger.pval), round_sci) %>%
  mutate(pt = as.character(pt),
         nsnp = nsnp + n_outliers,
         IVW = paste0(IVW_b, ' (', IVW_se, ')'),
         `MR-Egger` = paste0(Egger_b, ' (', Egger_se, ')', Egger_Signif),
         `Weighted median` = paste0(WME_b, ' (',WME_se, ')', WME_Signif),
         `Weighted mode` = paste0(WMBE_b, ' (',WMBE_se, ')', WMBE_Signif)) %>%
  select(outcome, exposure, outcome.name, exposure.name, pt, nsnp, n_outliers,
         snp_r2.exposure, snp_r2.outcome, correct_causal_direction, steiger_pval,
         # starts_with("IVW"), qval, starts_with("WME"), starts_with("WMBE"), starts_with("Egger"),
         IVW, qval, `MR-Egger`, `Weighted median`, `Weighted mode`,
         MRPRESSO.pval, Egger.pval, pass, pass_0.1)  %>%
  DT::datatable(caption = "Table 6: Significant Causal Effects",
                options = list(
                pageLength = 5, autoWidth = TRUE, scrollX = T
                )
  )


```

```{r, write-publication-results, echo=FALSE, eval=TRUE}
write_csv(out.final, glue("results/{model}/All/{model}_PublicationRes_{DATE}.csv"))
```

## Heatmap

```{r dat-plot}

## Dataframe for ploting
dat.plot <- exposures_outcomes %>%
  left_join(mr_best) %>%
  mutate(q_signif = as.character(signif.num(qval))) %>%
  mutate(z = IVW_b/IVW_se) %>%
  mutate(out = ifelse(qval < 0.1, paste0(round(IVW_b, 3), '\n', '(', round_sci(qval), ')'), " ")) %>%
  select(outcome, exposure, exposure.name, outcome.name, domain.exposure, domain.outcome, z, q_signif, out, pass, pass_0.1) %>%
  arrange(domain.exposure, desc(domain.outcome), outcome.name, exposure.name) %>%
  mutate(outcome.name = fct_inorder(outcome.name)) %>%
  mutate(exposure.name = fct_inorder(exposure.name)) %>%
  group_by(domain.exposure, domain.outcome) %>%
  arrange(exposure, outcome) %>%
  mutate(outcome.name = fct_inorder(fct_drop(outcome.name))) %>%
  mutate(exposure.name = fct_inorder(fct_drop(exposure.name))) %>%
  mutate(outcome1 = as.integer(fct_inorder(fct_drop(outcome.name)))) %>%
  mutate(exposure1 = as.integer(fct_inorder(fct_drop(exposure.name)))) %>%
  ungroup()
```

```{r heatmap,  fig.fullwidth=TRUE}
p1 <- ggplot(dat.plot) +
  geom_raster(aes(x = exposure.name, y = outcome.name, fill = z)) +
  facet_grid(domain.outcome ~ domain.exposure, scales = "free", space = "free", switch = "y") +
  geom_text(data = dat.plot, size = 4, aes(label = q_signif, x = exposure.name, y = outcome.name)) +
  scale_fill_gradient2(low="steelblue", high="firebrick", mid = "white", na.value = "grey50") +
#  coord_fixed() +
  theme_classic() +
  geom_vline(xintercept=seq(0.5, 23.5, 1),color="white") +
  geom_hline(yintercept=seq(0.5, 11.5, 1),color="white") +
  geom_rect(data=filter(dat.plot, pass_0.1 == TRUE), size=0.5, fill=NA, colour="orange",
            aes(xmin=exposure1 - 0.5, xmax=exposure1 + 0.5, ymin=outcome1 - 0.5, ymax=outcome1 + 0.5)) +
  geom_rect(data = filter(dat.plot, pass == TRUE), size=0.5, fill=NA, colour="red",
            aes(xmin=exposure1 - 0.5, xmax=exposure1 + 0.5,
                ymin=outcome1 - 0.5, ymax=outcome1 + 0.5)) +
  theme(legend.position = 'right', legend.key.height = unit(2, "line"),
        axis.text.x = element_text(angle = 35, hjust = 0), aspect.ratio=1,
        legend.title = element_blank(), legend.text = element_text(hjust = 1.5), text = element_text(size=10),
        axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_x_discrete(position = "top")
p1

```

```{r, eval=TRUE}
if(nrow(exposure.df) < nrow(outcome.df)){
  ggsave(glue("results/{model}/All/{model}_heatmap{DATE}.png"), plot = p1, width = 7, height = 11, units = "in")
} else if(nrow(exposure.df) > nrow(outcome.df)){
  ggsave(glue("results/{model}/All/{model}_heatmap{DATE}.png"), plot = p1, width = 11, height = 7, units = "in")
}

```
